IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/concrete.tex
Spelling
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

Unfortunately, an isomorphism is often too strong of a requirement.
To obtain an isomorphism with our single heap semantics, we need to mimic the
behavior of several heaps with a single actual heap.
The interesting cases are when we sandbox
an expression and when messages are sent and received.
The rule for sandboxing is
parameterized by the strategy |klone| (cf.\ Section~\ref{sec:retrofit}),
which defines what heap the new task
should execute with.  We have considered two choices:

@@

To this end, we represent addresses in the concrete language as
pairs $(|id|,|ta|)$ where |id| is a task identifier, and |ta| an
address in the abstract system\footnote{Note that this does
  not make the isomorphism trivial, as in the single heap, there
  is nothing preventing task 1 to access an address (2,|ta|).
  Furthermore, it is common to represent addresses in this way
  for efficient garbage collection of dead tasks.}.
We also formulate the following well-formedness condition for
configurations:
\[
  |wf c| = \forall |oneheapfullconf id il ie| \in |ic|.\ 
  \{ (|id'|,|ie'|) \in \mathcal{AV}(|ie|) \ \vert\ |id| \neq |id'| \} = \emptyset
\]
Essentially, every address in a given task must have the correct
identifier as the first part of the address.  It is easy to
see that the initial configuration satisfies this condition, and
any step in the concrete semantics preserves the condition.
Therefore, we only need to consider well-formed configurations,
which allows us to give the two required functions
|f| and |finv| for the isomorphism.  For conciseness, we informally
give their definition and leave the straight-forward proof that they
actually provide an isomorphism.
\begin{itemize}
  \item Addresses can be directly translated with
  $|f|((|id|,|ta|))=|ta|$, and $|finv|(|ta|)=|(id,ta)|$ for
  an address |ta| that occurs in task |id|.
  \item |f| splits the single heap into multiple heaps based on
  the |id| of the addresses.  |finv| produces a single heap
  by translating the addresses and collapsing everything to a single
  store.
\end{itemize}

>>>>

Unfortunately, an isomorphism is often too strong of a requirement.
To obtain an isomorphism with our single heap semantics, we need to mimic the
behavior of several heaps with a single actual heap.
The interesting cases are when we sandbox
an expression and when messages are sent and received.
The rule for sandboxing is
parametrized by the strategy |klone| (cf.\ Section~\ref{sec:retrofit}),
which defines what heap the new task
should execute with.  We have considered two choices:

@@

To this end, we represent addresses in the concrete language as
pairs $(|id|,|ta|)$ where |id| is a task identifier, and |ta| an
address in the abstract system\footnote{Note that this does
  not make the isomorphism trivial, as in the single heap, there
  is nothing preventing task 1 to access an address (2,|ta|).
  Furthermore, it is common to represent addresses in this way
  for efficient garbage collection of dead tasks.}.
We also formulate the following well-formedness condition for
configurations:
\[
  |wf c| = \forall |oneheapfullconf id il ie| \in |ic|.\ 
  \{ (|id'|,|ie'|) \in \mathcal{AV}(|ie|) \ \vert\ |id| \neq |id'| \} = \emptyset
\]
Essentially, every address in a given task must have the correct
identifier as the first part of the address.  It is easy to
see that the initial configuration satisfies this condition, and
any step in the concrete semantics preserves the condition.
Therefore, we only need to consider well-formed configurations,
which allows us to give the two required functions
|f| and |finv| for the isomorphism.  For conciseness, we only give
the interesting parts of their definition,
and leave the straight-forward proof that they
actually provide an isomorphism.
\begin{itemize}
  \item Addresses can be directly translated with
  $|f|((|id|,|ta|))=|ta|$, and $|finv|(|ta|)=|(id,ta)|$ for
  an address |ta| that occurs in task |id|.
  \item |f| splits the single heap into multiple heaps based on
  the |id| of the addresses.  |finv| produces a single heap
  by translating the addresses and collapsing everything to a single
  store.
\end{itemize}
